\framework: Morphology-based Entity and Relational Entity Extraction Framework for Arabic

### 2018-03-18 tex/merf/TALMajor/tool.tex
added availability

>>>>

\subsection{Framework Availability}
\framework is an open source tool present on google code under atmine repository (\url{https://code.google.com/p/atmine/}).
In addition to \framework, the repository contains entity extraction tasks developed by our research group.
People are welcome to download and use the tools.
We appreciate any feedback that we get and we try to improve the tools accordingly.
